---
title: "Tests shiny application"
author: "Caspar Sylwan, Nitin Kumar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tests shiny application}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The Riksbank is Sweden's central bank. We have used data from Riksbank for our shiny application.   

## Vignette Info

The shiny application compares four curves for demonstrative purposes.

## Euro market rates
As per Riksbank, the euro market is a loan market without underlying collateral with fixed-term deposits, with the highest time limit being one year. It is mostly a part of the interbank trading where the rates applying for some of the main currencies in the local interbank market, i.e. the banks' internal market for trade in currencies and debt securities, can be followed.

Euro market rates with 3-month duration includes:
USA
Japan
UK
Euro area
Norway
Denmark

For our lab exercise, we have only included Euro market rates with 3-month duration for Norway, USA, Japan, and Euro area.     
Euro market rates with 3-month duration for Norway

```{r, fig.show='hold'}
library(ggplot2)
library(labfifthcasnit)
library(dplyr)
library(httr)
library(readr)
library(lubridate)
rates_obj<-shiny_api$new()
rates<-rates_obj$riks_api()
EU<-filter(rates,Series=="EU 3M")
ggplot() + geom_point(data = EU, aes(x = date, y = Value))
      
```

Euro market rates with 3-month duration for USA

```{r, fig.show='hold'}
library(ggplot2)
library(labfifthcasnit)
library(dplyr)
library(httr)
library(readr)
library(lubridate)

rates_obj<-shiny_api$new()
rates<-rates_obj$riks_api()
US<-filter(rates,Series=="US 3M")
ggplot() + geom_point(data = US, aes(x = date, y = Value))

```


